Action alternatives & confidence factor

### 2023-03-29 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
sjt

@@

# merge data frames
# put all data frames into list
df_list <- list(df_sri, df_alternatives_count, df_alternatives_nd)

@@

```{r}
# confidence factor
describeBy(main$confidence_factor, main$id)
plot_confi <- boxplot(confidence_factor ~ id, data = main)

@@

@@

nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, corr.nov$count, method=c("pearson"))
print(nov_confi_count_corr, short = F)

@@

exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, corr.exp$count, method=c("pearson"))
print(exp_confi_count_corr, short = F)

@@

# novices: correlation between confidence factor and non-disruptive alternatives
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor, corr.nov$nd, method=c("pearson"))
print(nov_confi_nd_corr, short = F)

# experts: correlation between confidence factor and non-disruptive alternatives
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor, corr.exp$nd, method=c("pearson"))
print(exp_confi_nd_corr, short = F)

@@

>>>>

# SJT CM
df_sjt <- read_csv2(file = "data/SJT.csv",
                    locale = locale(decimal_mark = ",")) %>% 
  select(UI06_05,
         SJT_KF_gek) %>%
  filter(UI06_05 %in% c(101:126, 201:228),
         !UI06_05 %in% c(204, 226)
         ) %>% 
  na.omit() %>% 
  rename("id" = "UI06_05",
         "sjt" = "SJT_KF_gek")

@@

# merge data frames
# put all data frames into list
df_list <- list(df_sri,
                df_sjt,
                df_alternatives_count,
                df_alternatives_nd)

@@

# descriptives & plots
```{r}
# confidence factor
describeBy(main$confidence_factor, main$id)
plot_confi <- boxplot(confidence_factor ~ id, data = main)

# sjt cm
describeBy(main$sjt, main$id)
plot_confi <- boxplot(sjt ~ id, data = main)

@@

# sjt x count of action alternatives
```{r}
main %>% 
  filter(!is.na(sjt) | !is.na(count)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = sjt,
                       y = count,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "SJT Classroom Management",
       y = "Count of action alternatives") +
  theme_cowplot()

# sjt x non-disruptive action alternatives
```{r}
main %>% 
  filter(!is.na(sjt) | !is.na(nd)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = sjt,
                       y = nd,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "SJT Classroom Management",
       y = "Non-disruptive action alternatives") + 
  theme_cowplot()

# t-test and effect size
```{r}

#### confidence factor
# t-test for expertise differences
t.test(x = main$confidence_factor[main$id == "Expert"],
       y = main$confidence_factor[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$confidence_factor[main$id == "Expert"],
       y = main$confidence_factor[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives count
# t-test for expertise differences
t.test(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"],
       na.rm = TRUE)

### action alternatives non-disruptive
# t-test for expertise differences
t.test(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       na.rm = TRUE)
```

@@

nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, 
                                 corr.nov$count, 
                                 method=c("pearson"),
                                 adjust="holm")
print(nov_confi_count_corr, 
      short = F)

@@

exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, 
                                 corr.exp$count, 
                                 method=c("pearson"),
                                 adjust="holm")
print(exp_confi_count_corr, 
      short = F)

@@

###################################################

# novices: correlation between confidence factor and non-disruptive alternatives
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_nd_corr,
      short = F)

@@

###################################################

# novices: correlation between sjt and count
nov_sjt_count_corr <- cor.test(corr.nov$sjt,
                              corr.nov$count, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_sjt_count_corr, 
      short = F)

# experts: correlation between sjt and count
exp_sjt_count_corr <- cor.test(corr.exp$sjt,
                              corr.exp$count, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_sjt_count_corr,
      short = F)

# full sample: correlation between sjt and count
full_sjt_count_corr <- corr.test(main$sjt, 
                                 main$count, 
                                 method=c("pearson"), 
                                 adjust="holm")
print(full_sjt_count_corr, 
      short = F)

###################################################

# novices: correlation between sjt and non-disruptive alternatives
nov_sjt_nd_corr <- cor.test(corr.nov$sjt,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_sjt_nd_corr, 
      short = F)

# experts: correlation between sjt and non-disruptive alternatives
exp_sjt_nd_corr <- cor.test(corr.exp$sjt,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_sjt_nd_corr,
      short = F)

# full sample: correlation between sjt and non-disruptive alternatives
full_sjt_nd_corr <- corr.test(main$sjt,
                              main$nd,
                              method=c("pearson"),
                              adjust="holm")
print(full_sjt_nd_corr,
      short = F)
